\documentclass[a5paper]{article}
\usepackage{amsmath}
\usepackage[top=1cm,right=1cm,bottom=1cm,left=1cm]{geometry}
\setlength\parindent{0pt}
\setlength\parskip{1em}
%
%\usepackage{xcolor}
%\pagecolor[rgb]{0.1,0.1,0.1}
%\color[rgb]{1.0,1.0,1.0}
%
\begin{document}
\newcommand   \C           {\mathbf{C}}
\newcommand   \R           {\mathbf{R}}
\renewcommand \L           {\mathcal{L}}
\newcommand   \F           {\mathbf{F}}
\renewcommand \P           {\mathcal{P}}
\newcommand   \M           {\mathcal{M}}
\newcommand   \op          {\operatorname}

    3.A.14.
    Suppose $V$ is finite-dimensional with $\op{dim}V > 0$, and suppose $W$ is infinite-dimensional.
    Prove that $\L(V,W)$ is infinite-dimensional.

    Suppose $v_1,\dots,v_n$ is a basis of $V$.
    Suppose $T_1,\dots,T_m \in \L(V,W)$.

    For $T \in \op{span}(T_1,\dots,T_m)$ and $v \in V$, there exist $a_1,\dots,a_m,b_1,\dots,b_n \in \F$ such that
\begin{align*}
        T &= a_1T_1+\dots+a_mT_m \quad \text{and} \\
        v &= b_1v_1+\dots+b_nv_n .
\end{align*}
    Thus
\begin{align*}
        Tv &= T(b_1v_1+\dots+b_nv_n) \\
           &= b_1Tv_1 + \dots + b_nTv_n \\
           &= b_1(a_1T_1+\dots+a_mT_m)v_1 + \dots + b_n(a_1T_1+\dots+a_mT_m)v_n \\
           &= a_1b_1T_1v_1+\dots+a_mb_1T_mv_1 + \dots + a_1b_nT_1v_n+\dots+a_mb_nT_mv_n .
\end{align*}
    Hence any vector in $\op{range}T$ is a linear combination of the list of vectors
\begin{equation*}
        T_1v_1,\dots,T_mv_1, \dots, T_1v_n,\dots,T_mv_n .
\end{equation*}
    No list spans $W$ because $W$ is infinite-dimensional.
    So there exists $w \in W$ such that $w$ cannot be written as a linear combination of this list of vectors.

    Define $S \in \L(V,W)$ such that $Sv_1=w$ and $Sv_j=0$ for $2 \le j \le n$.

    To see that it is not possible to write $S$ as a linear combination of $T_1,\dots,T_m$, suppose that it is possible.
    Then there exist $c_1,\dots,c_m \in \F$ such that
\begin{align*}
        c_1T_1 + \dots + c_mT_m = S .
\end{align*}
    Applying both sides of the equation to $v_1$,
\begin{align*}
        (c_1T_1 + \dots + c_mT_m)v_1  &= Sv_1 \\
        c_1T_1v_1 + \dots + c_mT_mv_1 &= w .
\end{align*}
    This is a contradiction because the left side of the equation is a linear combination of the list of vectors that we defined $w$ not to be in the span of.

    To recap, for any list of linear maps from $V$ to $W$, there is another linear map from $V$ to $W$ not in the span of the list.
    Hence no list spans $\L(V,W)$.
    Thus $\L(V,W)$ is infinite-dimensional.
\end{document}
